Summary Tables

### 2023-04-28 summary_tables.Rmd
Update scenario names

```{r warning=FALSE, echo=F, message=FALSE}

dat <- list()

dat[[city]] <- io[[city]]$trip_scen_sets %>% 
  mutate(scenario = case_when(
    scenario == "Scenario 1" ~ "CYC_SC", 
    scenario == "Scenario 2" ~ "CAR_SC",
    scenario == "Scenario 3" ~ "BUS_SC",
    scenario == "Scenario 4" ~ "MOT_SC",
    scenario == "Baseline" ~ "Baseline")) %>% 
  group_by(scenario, trip_mode, trip_distance_cat) %>% 
  summarise(n = dplyr::n(), dist = sum(trip_distance, na.rm = T)) %>% 
  mutate(city = city)

td <- dat[[city]]

for (i in 1:nrow(td)) {
    val <- td %>% filter(scenario == "Baseline", trip_mode == td$trip_mode[i] & 
                           trip_distance_cat == td$trip_distance_cat[i] &
                           city == td$city[i])

    if (nrow(val) > 0) {
      td$diff[i] <- val$n - td$n[i]
      td$trip_prop[i] <- round(td$n[i] / val$n, 2)
      td$dist_prop[i] <- round(td$dist[i] / val$dist, 2)

    }
}

dat[[city]] <- td

write_csv(bind_rows(dat), "results/multi_city/scen_prop.csv")

@@

  td <- io[[city]]$outcomes$mmets %>% dplyr::select(ends_with("mmet")) %>%
    rename("Baseline" = base_mmet, "CYC_SC" = scen1_mmet,
           "CAR_SC" = scen2_mmet,  "BUS_SC" = scen3_mmet) %>% 
    summarise(across(, ~ quantile(.x, c(0.05,0.10,0.25, 0.375, 0.50,0.75,0.90), na.rm = T)), 
              prob = c(0.05,0.10,0.25, 0.375, 0.50,0.75,0.90)) %>%
    pivot_longer(cols = -c(prob)) %>% mutate(city = city)

  td1 <- io[[city]]$outcomes$mmets %>% dplyr::select(ends_with("mmet")) %>%
    rename("Baseline" = base_mmet, "CYC_SC" = scen1_mmet,
           "CAR_SC" = scen2_mmet,  "BUS_SC" = scen3_mmet) %>% 
    summarise(across(, ~ mean(.x))) %>%  t() %>% as.data.frame() %>% 
    tibble::rownames_to_column("name") %>% 
    rename(value = V1) %>% 
    mutate(prob = "mean") %>% mutate(city = city)

@@

}
write_csv(data.table::rbindlist(l), "results/multi_city/PA/pa_distr.csv")
```

>>>>

# ```{r warning=FALSE, echo=F, message=FALSE}
# 
# dat <- list()
# 
# for (city in cities) {
#   
# dat[[city]] <- io[[city]]$trip_scen_sets %>% 
#   mutate(scenario = case_when(
#     scenario == "Scenario 1" ~ "CYC_SC", 
#     scenario == "Scenario 2" ~ "CAR_SC",
#     scenario == "Scenario 3" ~ "BUS_SC",
#     scenario == "Scenario 4" ~ "MOT_SC",
#     scenario == "Baseline" ~ "Baseline")) %>% 
#   group_by(scenario, trip_mode, trip_distance_cat) %>% 
#   summarise(n = dplyr::n(), dist = sum(trip_distance, na.rm = T)) %>% 
#   mutate(city = city)
# 
# td <- dat[[city]]
# 
# for (i in 1:nrow(td)) {
#     val <- td %>% filter(scenario == "Baseline", trip_mode == td$trip_mode[i] & 
#                            trip_distance_cat == td$trip_distance_cat[i] &
#                            city == td$city[i])
#     
#     if (nrow(val) > 0) {
#       td$diff[i] <- val$n - td$n[i]
#       td$trip_prop[i] <- round(td$n[i] / val$n, 2)
#       td$dist_prop[i] <- round(td$dist[i] / val$dist, 2)
#       
#     }
# }
# 
# dat[[city]] <- td
# 
# }
# 
# write_csv(bind_rows(dat), "results/multi_city/scen_prop.csv")
# 
# ```

@@

  td <- io[[city]]$outcomes$mmets %>% dplyr::select(ends_with("mmet")) %>%
    rename("Baseline" = base_mmet, "CYC_SC" = sc_cycle_mmet,
           "CAR_SC" = sc_car_mmet,  "BUS_SC" = sc_bus_mmet,
           "MOT_SC" = sc_motorcycle_mmet) %>% 
    summarise(across(, ~ quantile(.x, c(0.05,0.10,0.25, 0.375, 0.50,0.75,0.90), na.rm = T)), 
              prob = c(0.05,0.10,0.25, 0.375, 0.50,0.75,0.90)) %>%
    pivot_longer(cols = -c(prob)) %>% mutate(city = city)

  td1 <- io[[city]]$outcomes$mmets %>% dplyr::select(ends_with("mmet")) %>%
     rename("Baseline" = base_mmet, "CYC_SC" = sc_cycle_mmet,
           "CAR_SC" = sc_car_mmet,  "BUS_SC" = sc_bus_mmet,
           "MOT_SC" = sc_motorcycle_mmet) %>% 
    summarise(across(, ~ mean(.x))) %>%  t() %>% as.data.frame() %>% 
    tibble::rownames_to_column("name") %>% 
    rename(value = V1) %>% 
    mutate(prob = "mean") %>% mutate(city = city)

@@

}
# write_csv(data.table::rbindlist(l), "results/multi_city/PA/pa_distr.csv")
```
